Revisiting Short-Chain Fatty Acids and the Microbiota in Colorectal Cancer

### 2018-05-23 submission/manuscript.Rmd
add conclusion statement

>>>>

Our observations conssitently found no difference in SCFA concentration between individuals with normal colons and patients with either adenoma or carcinoma tumors. Although these results are different than other reports in the literature, they do align with the randomized controlled trials that have tested fiber use in preventing colorectal tumor recurrence. Overall, these results suggest that the SCFAs produced by resident microbes do not protect against tumor. By focusing on other types of metabolites, the identification of more promising therapeutic options for use in treating colorectal cancer may be found.
